Untitled

### 2017-11-23 PaperCode.Rmd
Not sure
Bunch of small changes

decile <- bind_rows(mutate(unaffordExLon, type = "Excluding London"), 
                    mutate(unafford, type = "Including London"),
                    mutate(unaffordLon, type = "Only London")) %>%
    group_by(type) %>%
    mutate(decile = ntile(ratio, 50)) %>%
      group_by(decile, type) %>%
    summarise(mean = mean(LowUsePerc),
              median = median(LowUsePerc),
              counts = n()
              )

@@

decile %>% ggplot(aes(x= decile, y = median)) + 
  facet_grid(.~type) + 
  #geom_point(data =unaffordExLon , aes(x= decile, y = LowUsePerc), alpha = 0.2 )+
  geom_point(aes(colour = type))  +
  labs(x = "ith 2 percentile group", y = "median Percent Low Use") + 
  theme(legend.position= "none") + 
  geom_smooth(method="loess",se=FALSE, colour = "black")
SaveFig("LowUsePercVSratio.pdf")

@@

>>>>

decile <- bind_rows(mutate(unaffordExLon, type = "Excluding London"), 
                    mutate(unafford, type = "Including London"),
                    mutate(unaffordLon, type = "Only London")) %>%
    group_by(type) %>%
    mutate(decile = ntile(ratio, 50)) %>%
      group_by(decile, type) %>%
    summarise(mean = mean(LowUsePerc),
              median = median(LowUsePerc),
              counts = n(),
              ratio= mean(ratio)
              ) %>%
  mutate(decile2 = decile^2,
         ratio2 = ratio^2,
         logval = log(decile),
         expval = exp(decile),
         expvalneg = exp(-decile)) %>%
  filter(!is.na(decile))

@@

decile %>% 
#  filter(type == "Only London") %>% 
  ggplot(aes(x= decile, y = median)) + 
  facet_grid(.~type) + 
  #geom_point(data =unaffordExLon , aes(x= decile, y = LowUsePerc), alpha = 0.2 )+
  geom_point(aes(colour = type))  +
  labs(x = "2 percentile group", y = "median Percent Low Use") + 
  theme(legend.position= "none") + 
  geom_smooth(method="loess",se=FALSE, colour = "black")
SaveFig("LowUsePercVSratio.pdf")

decile %>% 
  filter(type == "Including London") %>% 
  ggplot(aes(x= ratio, y = median)) + 
  facet_grid(.~type) + 
  #geom_point(data =unaffordExLon , aes(x= decile, y = LowUsePerc), alpha = 0.2 )+
  geom_point(aes(colour = type))  +
  labs(x = "ith 2 percentile group", y = "median Percent Low Use") + 
  theme(legend.position= "none") + 
  geom_smooth(method="loess",se=FALSE, colour = "black")

#model fit
decile %>% 
    filter(type == "Excluding London") %>% 
  lm(median~decile +decile2, data = .) %>% summary

#model fit
decile %>% 
    filter(type == "Excluding London") %>% 
lm(median~ratio + ratio2, data = .) %>% summary

decile %>% 
    filter(type == "Excluding London") %>% 
lm(median~expval + expvalneg, data = .) %>% summary

#make nonlinear  model
mod <- decile %>% 
    filter(type == "Excluding London") %>% 
  nls(median ~ exp(a + b*decile)+  exp(d + c*decile), data = ., 
      start = list(a = 0, b = -3, c = 0, d = 0))

mod2 <- decile %>% 
    filter(type == "Only London") %>% 
  nls(median ~ exp(a + b*decile), data = ., 
      start = list(a = 0, b = -3))

summary(mod)

decile %>%
      filter(type == "Excluding London") %>% 
  ggplot(aes(x = decile, y = median))+
  geom_point() +
  geom_line(aes(y = predict(mod, list(x = decile))))

@@

Big Stats
```{r}

### 2017-11-23 testCode.Rmd
Not sure
Bunch of small changes

Offshore2 <- Offshore %>%
    select(Property_Address, Postcode) %>%
    mutate(streetAddress = str_split(Offshore$Property_Address, ",", n = 2) %>% 
  map_chr(~.x[1]),
           Postcode = gsub(" ", "",Postcode))

@@

#need another regex which looks at number and if followed by apartement etc uses the number as the flat number
Flatregex <- "(the.+)?(flat|apartment|penthouse)(s)?(\\s(no)?(.+?)(\\s|,)(\\s?(to|-)\\s?.+?(\\s|,))?|,)"

Flats <- Offshore2 %>%
  filter(grepl("flat|apartment|penthouse", Property_Address, ignore.case = T))%>%
  mutate(FlatNumber = str_extract(tolower(Property_Address), 
            Flatregex) %>%
           sub("\\s$|,$", "", .)
)

# (the.+)?(flat|apartment|penthouse)(s)?(\\s(.+?)(\\s|,)(\\s?(to|-)\\s?.+?(\\s|,))?|,)
# 
# some flats start with a "the eastern" or "the penthouse" this is optional
# (the.+)?
# 
# the main expression it has to say this! optioanl "s" on the end
# (flat|apartment|penthouse)(s)?
#
#the additional matching characteristics these come either side of and or statement
# ((s)?\\s(.+?)(\\s|,)(\\s?(to|-)\\s?.+?(\\s|,))?|,)
# (A|B)
# 
# 
# A = \\s(.+?)(\\s|,)(\\s?(to|-)\\s?.+?(\\s|,))?
# A = (A1)(A2)
# 
# space followed by some characters followed by a space or a comma this extracts the flat number eg "flat c"
# A1 = \\s(.+?)(\\s|,)
# 
# optional space then either "to" or "-" followed by optional space followed by some characters followed by space or comma. This is to catch things like "flats 1 to 5" or flat 4-6
# A2 = (\\s?(to|-)\\s?.+?(\\s|,))?
# 
# This is simple some are simply called "flat"  or "the penthouse" this catches those
# B = ,

@@

test <- Flats2 %>%
  filter(grepl("Dolphin Square", address2, ignore.case = TRUE))

@@

test2 <- test %>%
  group_by(Endings) %>%
  summarise(count = n())

@@

#create the regex string to match
Wordswithapotrophes <- paste0("(( \\w+)('s)?)+ (",paste(c(Road2$Endings),  collapse = "|"),")")
roadmatchregex <- paste0("([0-9]+)", Wordswithapotrophes)

@@

StreetNum <- str_extract(tolower(Offshore2$Property_Address), roadmatchregex )

Offshore3 <- Offshore2 %>% 
  mutate(
    Property_Address =  gsub(" \\(.+?\\)", "", Property_Address),
    class = case_when(
    grepl(Flatregex, Property_Address, ignore.case = T) ~ "domestic",
    grepl("^car |^park", Property_Address, ignore.case = T) ~"parking space",
    grepl("^land", Property_Address, ignore.case = T) ~ "land",
    grepl("^[a-z]+( [a-z])* cottage", Property_Address, ignore.case = T) ~"domestic",
    grepl("(^[0-9]+)(( \\w+)('s)?)+ (court|villas)", Property_Address, ignore.case = T) ~"domestic",
    TRUE ~ "unknown"
  )) %>%
  mutate(Streetadd = StreetNum,
    Streetnumber =gsub("[a-z]", "", StreetNum, ignore.case = T), 
         Street = gsub("[0-9]", "", StreetNum),
    Street = case_when(
      !is.na(Street) ~ Street,
      grepl("^land", Property_Address, ignore.case = T) ~ 
        str_extract(tolower(Property_Address), paste0("(of|at)", Wordswithapotrophes) ) %>%
        gsub("(of |at )", "",.), #begins with land about 13k
      grepl("( \\w+)+(way|gate,)", Property_Address, ignore.case = T) ~ #roadds that er blblablaGATE
        str_extract(tolower(Property_Address), "( \\w+)+(way|gate)," ),
      #Fixing for knightsbridge
       grepl("knightsbridge", Property_Address, ignore.case = T) ~ "knightsbridge",
      grepl("holland", Property_Address, ignore.case = T) ~ "holland",
      TRUE ~ str_extract(tolower(Property_Address), Wordswithapotrophes ) #no street number
    )
    )

test<- Offshore3%>%
  #sorting houses
  mutate(
    HouseName = str_extract(tolower(Property_Address), "^[a-z]+( [a-z])* house")

    )

grep("( \\w+)+(way|gate),", " parkway,")

table(is.na(Offshore3$Street))
table(is.na(Offshore3$Streetnumber))

table(Offshore3$class)

#Everything that is not land about 7000 items 
  test <- Offshore3 %>%
  filter(is.na(Street))  %>%
  filter(grepl(paste0("^[^(land)]"), Property_Address, ignore.case = TRUE))

@@

@@

    CompanyHouse <- CompanyData %>%
      mutate(House = tolower(X10)) %>%
  filter(grepl("house", House))

 test <-    CompanyHouse %>%
      filter(grepl( "Darcy House",  House, ignore.case = T))

@@

>>>>

Offshore2 <- Offshore %>%
    select(Property_Address, Postcode) %>%
    mutate(Postcode = gsub(" ", "",Postcode))

@@

#need another regex which looks at number and if followed by apartement etc uses the number as the flat number
Flatregex <- "(the.+)?(flat|apartment|penthouse)(s)?(\\s(no)?(\\S+?)(\\s|,)(\\s?(to|-)\\s?.+?(\\s|,))?|,)"

Flats <- Offshore2 %>%
  filter(grepl(Flatregex , Property_Address, ignore.case = T))%>%
  mutate(FlatNumber = str_extract(tolower(Property_Address), 
            Flatregex) %>%
           sub("\\s$|,$", "", .)
)

(flat|apartment|penthouse)(s)?

# (the.+)?(flat|apartment|penthouse)(s)?(\\s(.+?)(\\s|,)(\\s?(to|-)\\s?.+?(\\s|,))?|,)
# 
# some flats start with a "the eastern" or "the penthouse" this is optional
# (the.+)?
# 
# the main expression it has to say this! optional "s" on the end
# (flat|apartment|penthouse)(s)?
#
#the additional matching characteristics these come either side of and or statement
# ((s)?\\s(\S+?)(\\s|,)(\\s?(to|-)\\s?.+?(\\s|,))?|,)
# (A|B)
# 
# 
# A = \\s(\S+?)(\\s|,)(\\s?(to|-)\\s?.+?(\\s|,))?
# A = (A1)(A2)
# 
# space followed by anything that is not whitespace followed by a space or a comma this extracts the flat number eg "flat c"
# A1 = \\s(\S+?)(\\s|,)
# 
# optional space then either "to" or "-" followed by optional space followed by some characters followed by space or comma. This is to catch things like "flats 1 to 5" or flat 4-6
# A2 = (\\s?(to|-)\\s?.+?(\\s|,))?
# 
# This is simple some are simply called "flat"  or "the penthouse" this catches those
# B = ,

@@

#Use Dolphin Square to extract house names
test <- Flats2 %>%
  filter(grepl("Dolphin Square", address2, ignore.case = TRUE)) %>%
  mutate(address2 = str_extract(tolower(address2), "([a-z0-9]+)\\s(house)"))

@@

@@

#create the regex string to match
Wordswithapotrophes <- paste0("(( \\w+)('s)?)+ (",
                              paste(c(Road2$Endings, 
                                      "( \\w+)+(way|gate,)",
                                      "knightsbridge",
                                      "holland"
                                      ),  collapse = "|"),")")
roadmatchregex <- paste0("(([0-9]+([a-z])?))?", Wordswithapotrophes)

@@

#This is used in the next code cleaning block it is done here to keep the code easier to read
StreetNum <- str_extract(tolower(Offshore2$Property_Address), roadmatchregex )

Offshore3 <- Offshore2 %>% 
  mutate(
    Property_Address =  gsub(" \\(.+?\\)", "", Property_Address), #remove anything in brackets e.g postcodes
    #Label some classes
    class = case_when( 
    grepl(Flatregex, Property_Address, ignore.case = T) ~ "domestic",
    grepl("^car |^park", Property_Address, ignore.case = T) ~"parking space",
    grepl("^land", Property_Address, ignore.case = T) ~ "land",
    grepl("^[a-z]+( [a-z])* cottage", Property_Address, ignore.case = T) ~"domestic",
    grepl("(^[0-9]+([a-z])?)(( \\w+)('s)?)+ (court|villas|mansions)", Property_Address, ignore.case = T) ~"domestic",
    TRUE ~ "unknown"
  )) %>%
  #Do Streets
  mutate( Street = gsub("([0-9]+([a-z])?)", "", StreetNum),
          Streetnumber =gsub("([a-z])+", "", StreetNum, ignore.case = T),
          Street = case_when(
      !is.na(Street) ~ Street, #if not NA keep as is otherwise...
      TRUE ~ str_extract(tolower(Property_Address), Wordswithapotrophes ) #no street number
    ),
    Street = case_when(
            grepl("^land", Property_Address, ignore.case = T) ~ 
        str_extract(tolower(Property_Address), paste0("(of|at)", Wordswithapotrophes) ) %>%
          gsub("of |at ", "",.), #begins with land about 13k
        TRUE ~ Street

    ) %>% gsub(" (and|to) ", "", .)
    ) %>%
  #sorting houses
  mutate(
    HouseName  = str_extract(tolower(Property_Address), "^([a-z]+)( [a-z]+)* (house|court|farm|villa|cottage|lodge)(s)?") %>%
      ifelse(grepl("^land",.), NA,.)

    ) %>%
#Trim whitspace
mutate(Street = trimws(Street))

@@

        OffshoreHouse <- Offshore %>%
  filter(grepl("house", tolower(Property_Address)))

@@

    CompanyHouse <- CompanyData %>%
      mutate(House = tolower(X8)) %>%
  filter(grepl("house", House))

 test <-    CompanyHouse %>%
      filter(grepl( "mansions",  House, ignore.case = T))

@@

#Split out VOA addresses

rm(columnnames)

#create street and number split out like for offshore
CompanyData2 <- CompanyData %>%
  rename(Property_Address = X8)

StreetNum <- str_extract(tolower(CompanyData2$Property_Address), roadmatchregex )

CompanyData2 <- CompanyData2 %>%
    mutate( Street = gsub("([0-9]+([a-z])?)", "", StreetNum),
          Streetnumber =gsub("([a-z])+", "", StreetNum, ignore.case = T),
          Street = case_when(
      !is.na(Street) ~ Street, #if not NA keep as is otherwise...
      TRUE ~ str_extract(tolower(Property_Address), Wordswithapotrophes ) #no street number
    ),
    Street = case_when(
            grepl("^land", Property_Address, ignore.case = T) ~ 
        str_extract(tolower(Property_Address), paste0("(of|at)", Wordswithapotrophes) ) %>%
          gsub("of |at ", "",.), #begins with land about 13k
        TRUE ~ Street

    ) %>% gsub(" (and|to) ", "", .)
    )

#overlapping street names
sum(unique(Offshore3$Street) %in% tolower(unique(CompanyData$X11)))

sum(unique(Offshore3$HouseName) %in% tolower(unique(CompanyData$X25)))

test <- Offshore3 %>%
  filter(HouseName %in% tolower(unique(CompanyData$X25)), !is.na(HouseName))

#match house name and street
StreetHouseComp <- tolower(paste(CompanyData$X11,CompanyData$X25)) %>% unique
StreetHouseOffshore <- tolower(paste(Offshore3$Street,Offshore3$HouseName))[!is.na(Offshore3$HouseName)] %>% unique

#Actual companies!
CompMatch <- CompanyData %>%
  filter(  tolower(paste(X11,X25)) %in% StreetHouseOffshore, is.na(X23)  )

OffshoreMatch <- Offshore3 %>%
  filter(paste(Street,HouseName) %in% StreetHouseComp, !is.na(HouseName))

OffshoreMatch2 <- Offshore3 %>%
  mutate(test = paste(Street,HouseName))
"matthew murray house"
name <- "matthew murray house"

Companyinfo <- CompanyData %>%
  filter(grepl(name, tolower(X25), ignore.case = T))

OffshoreInfo <-Offshore3 %>%
  filter(grepl(name, HouseName, ignore.case = T))

#match lsoa for offshore postcodes

```{r}
test <- Offshore %>%
  filter(!is.na(Postcode)) %>%
  mutate(Postcode = gsub(" ", "", Postcode)) %>%
  left_join(., CorePstCd, "Postcode")

table(is.na(test$lsoa11cd))

test2 <- test %>%
  filter(!is.na(lsoa11cd)) %>%
  group_by(lsoa11cd) %>%
  summarise(counts = n(),
            LAD11CD = first(LAD11CD),
            LAD11NM = first(LAD11NM),
            Admin_ward_code = first(Admin_ward_code),
            WD16NM = first(WD16NM)) %>%
  arrange(desc(counts))

examin <- test %>% 
  filter(lsoa11cd =="E01006854")

table(examin$Proprietor_Name_1)
```

#Improve geoloacation

```{r}
setwd(file.path(DataFolder, "GeoNames"))

columnnames <- "geonameid
name
asciiname
alternatenames
latitude
longitude
feature class
feature code
country code
cc2
admin1 code
admin2 code 
admin3 code
admin4 code
population
elevation
dem
timezone
modification date " %>% str_split(., "\n", simplify = T) %>% trimws

GeoNames <- read_tsv("GB.txt", col_names = FALSE) %>%
  setNames(columnnames)

MaxMind <- read_csv("worldcitiespop.txt")

test <- MaxMind %>%
  filter(Country == "gb")

test %>%
  filter(grepl("queens", City, ignore.case = TRUE) )

test <- GeoNames %>%
filter(grepl("queens", name, ignore.case = TRUE) )
